Tabular Constraint Learning

### 2016-04-14 Paper/ECAI/tabular.tex
Table

\newcommand{\numeric}[1]{\format{numeric}(#1)}
\newcommand{\textual}[1]{\format{textual}(#1)}
\newcommand{\integer}[1]{\format{integer}(#1)}
\newcommand{\length}[1]{\format{length}(#1)}
\newcommand{\nat}{\mathcal{N}}

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}
\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{XXX}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{v_x} & $\integer{v_x}$ or $\textual{v_x}$ & All elements in $v_x$ are different \\
    %X = Y & & \\
    \ecfkey{v_{fk}}{v_{pk}} & FK and PK have the same type; they originate from different tables and PK is all-different & all values in FK exist in PK \\
    % TODO check out
    \eclookupprod{v_r}{v_1}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \eclookup{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \eclookupfuzzy{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecperm{v_x} & & \\
    \ecprod{v_r}{v_1}{v_2} & & \\
    \ecproj{v_r}{\mathbf{v_x}} & & \\
    \ecrank{v_r}{v_x} & Y and X have the same length & Y is the rank of X (including ties)\\
    \ectotal{v_r}{v_{pos}}{v_{neg}} & A, P and N have the same length and their length is at least 2 & *\\
    \ecseries{v_x} & & \\
    \ecsumc{v_r}{\mathbf{v_x}} & & Y is the result of summing each column in X \\
    \ecsumr{v_r}{\mathbf{v_x}} & & Y is the result of summing each row in X \\
    \ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecsumprod{v_r}{v_1}{v_2} & & \\

\samuel{Motivate why product, not sum (=diff) you only need one, hardcoded preference for display}

  \end{tabularx}
  \caption{Spreadsheet Constraints \sergey{Here a detailed explanation on what is going on, what is essential, what is not? etc should be self-explanatory}}
  \label{table:constraints}
\end{table*}

>>>>

\newcommand{\numeric}{\format{numeric}}
\newcommand{\textual}{\format{textual}}
\newcommand{\integer}{\format{integer}}
\newcommand{\plength}{\format{length}}
\newcommand{\ptype}{\format{type}}
\newcommand{\ptable}{\format{table}}
\newcommand{\por}{\format{orientation}}
\newcommand{\nat}{\mathcal{N}}

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}
\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{l X X}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{v_x} & $\integer(v_x)$ or $\textual(v_x)$ & All elements in $v_x$ are different \\
    %X = Y & & \\
    \ecfkey{v_{fk}}{v_{pk}} & $\ptype(v_{fk})$ = $ptype(v_{pk})$,$\ptable(v_{fk}) \neq \ptable(v_{pk})$, $\ecalldiff{v_{pk}}$ & Every value in @fk also exist in @pk \\
    % TODO check out
    \eclookupprod{v_r}{v_1}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@r, @1, @fk\}$ and in $\{@pk, @val\}$ all have the same \plength, \ptable and \por.
      & $@r$ is the obtained by multiplying $@1$ with $\eclookup{@fk}{@pk}{@val}$  
      \\
    \eclookup{v_r}{v_{fk}}{v_{pk}}{v_{val}}
      & the variables in $\{@fk, @val\}$ and in $\{@pk, @r\}$ all have the same \plength, \ptable and \por; $@r$ and~$@val$ have the same type; and \ecfkey{@fk}{@pk}.
      & Lookup $@fk$ in $@pk$ and return the corresponding value in $@val$.
      \\
    \eclookupfuzzy{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecperm{v_x} & & \\
    \ecprod{v_r}{v_1}{v_2} & & \\
    \ecproj{v_r}{\mathbf{v_x}} & & \\
    \ecrank{v_r}{v_x} & Y and X have the same length & Y is the rank of X (including ties)\\
    \ectotal{v_r}{v_{pos}}{v_{neg}} & A, P and N have the same length and their length is at least 2 & *\\
    \ecseries{v_x} & & \\
    \ecsumc{v_r}{\mathbf{v_x}} & & Y is the result of summing each column in X \\
    \ecsumr{v_r}{\mathbf{v_x}} & & Y is the result of summing each row in X \\
    \ecsumif{v_r}{v_{fk}}{v_{pk}}{v_{val}} & & \\
    \ecsumprod{v_r}{v_1}{v_2} & & \\

  \end{tabularx}
  \caption{Spreadsheet Constraints \sergey{Here a detailed explanation on what is going on, what is essential, what is not? etc should be self-explanatory}\samuel{Motivate why product, not sum (=diff) you only need one, hardcoded preference for display}
}
  \label{table:constraints}
\end{table*}
